Cross-validation of regression models: mixed model examples (edited)

### 2023-10-11 scratch/gm_addition_to_cv-edited.Rmd
add errors/warnings/messages for bad reps and seed args to cv() methods

```{r cross-validation}
#| out.width = "100%",
#| fig.height = 6,
#| fig.cap = "Cross-validation comparing random intercept models with varying fixed effects and with case- and cluster-based resampling."
modlist <- models("~ 1"=fit0, "~ x"=fit1, "~ x + xm"=fit2)
cvs_cases <- cv(modlist, data=Data, seed=9693)
cvs_clusters <- cv(modlist, data=Data, cluster="group", seed=4576)

>>>>

```{r cross-validation}
#| out.width = "100%",
#| fig.height = 6,
#| fig.cap = "Cross-validation comparing random intercept models with varying fixed effects and with case- and cluster-based resampling."
modlist <- models("~ 1"=fit0, "~ x"=fit1, "~ x + xm"=fit2)
cvs_cases <- cv(modlist, data=Data, seed=9693)
cvs_clusters <- cv(modlist, data=Data, cluster="group")
